---
title: "House Prices - Kaggle"
url: "https://www.kaggle.com/c/house-prices-advanced-regression-techniques"
author: "André Rizzo"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    highlight: tango

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```



### Check if libraries are installed
```{r}
if (!require("tidyverse")) install.packages("tidyverse")
if (!require("here")) install.packages("here")
if (!require("RizzoEDA")) install.packages("RizzoEDA")
if (!require("dataMaid")) install.packages("dataMaid")
if (!require("DataExplorer")) install.packages("DataExplorer")
if (!require("corrplot")) install.packages("corrplot")
if (!require("skimr")) install.packages("skimr")

```


### Load libraries
```{r}
library(tidyverse)
library(here)
library(RizzoEDA)
library(dataMaid)
library(DataExplorer)
library(corrplot)
library(skimr)

```


### Load data
```{r}
path = here("data/raw/train.csv")
df_train = read_csv(path)
```


### Data Exploration


#### Check the dimensions of the data
```{r}

dim(df_train)
```


#### Check the first rows of the data
```{r}
head(df_train)
```


#### Check the last rows of the data
```{r}
tail(df_train)
```


#### Check the structure of the data
```{r}
df_train %>% 
  glimpse()

```

#### Identify numeric features names
```{r}
numeric_features_names = df_train %>% 
  select_if(is.numeric) %>%
  colnames()

numeric_features_names
```


#### Identify numeric features
```{r}
numeric_features = df_train %>% 
  select_if(is.numeric)

numeric_features
```

#### Identify categorical features names
```{r}
cat_features_names = df_train %>% 
  select_if(is.character) %>%
  colnames()

cat_features_names
```


#### Identify categorical features
```{r}
cat_features = df_train %>% 
  select_if(is.character)

cat_features
```



#### Check the summary of the data
```{r}
skim(df_train)
```

#### Check the missing values - Numeric Features
```{r}
numeric_features %>%
  plot_missing(ggtheme = theme_classic(), title = "Missing Values - Numeric Features")

```


#### Check the missing values - Categorical Features
```{r}
cat_features %>%
  plot_missing(ggtheme = theme_classic(), title = "Missing Values - Categorical Features")

```

#### Check categorical features
```{r}
df_train %>%
  plot_bar(ggtheme = theme_light(), title = "Categorical Data")
```

### Check numerical features

#### Check the distribution of the numerical features
```{r}
df_train %>%
  plot_histogram(ggtheme = theme_light(), title = "Numerical Data", nrow = 3, ncol = 3)
```

#### Density plot
```{r}
df_train %>%
  plot_density(ggtheme = theme_light(), title = "Density Plot", nrow = 3, ncol = 3)
```

#### qqplot
```{r}
df_train %>%
  plot_qq(ggtheme = theme_light(), title = "qqplot", nrow = 3, ncol = 3)
```

### Correlogram
```{r}
numeric_features %>%
  plot_correlation(ggtheme = theme_light(), title = "Correlogram")

```


### Check the correlation of the numeric features
```{r}
cor_matrix = cor(numeric_features, method = "spearman", use = "pairwise.complete.obs")

```

### Show what correlation coefficients are considered strong
```{r}
corrplot(cor_matrix, method = "circle", type = "full", tl.col = "black", tl.srt = 45, tl.cex = 0.5)
```


# Calculate the VIF
```{r}
vif = vif(numeric_features)
vif = vif[order(vif, decreasing = TRUE)]
vif
```

